---
title: "Lab3"
author: "Denys Kushnirenko"
date: "2023-11-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1. For two to four sets of interrelated data, construct a scatter plot, and determine the functional type of dependence from the graphs.

```{r, echo=FALSE}
happyscore_income <- read.csv(".\\happyscore_income.csv")
library(ggplot2)
library(car)
```
```{r}
plot(happyScore ~ GDP, data = happyscore_income, pch = 20, main = "The dependence of happiness level on the country's GDP")
plot(happyScore ~ avg_satisfaction, data = happyscore_income, pch = 20, main = "The dependence of happiness level on the level of satisfaction with income")

```

##  2. Construct the corresponding regression model.

```{r}
model1 <- lm(happyScore ~ GDP+avg_satisfaction, data = happyscore_income)
summary(model1)
```

## 3. Plot the obtained regression line on the same graph as the scatter plot.

```{r}
ggplot(data = happyscore_income) +
  geom_point(mapping = aes(x = GDP, y = happyScore, size = avg_satisfaction)) +
  geom_smooth(mapping = aes(x = GDP, y = happyScore), color = "red",
              method = "lm", formula = y ~ x, se = TRUE)
ggplot(data = happyscore_income) +
  geom_point(mapping = aes(x = avg_satisfaction, y = happyScore)) +
  geom_smooth(mapping = aes(x = avg_satisfaction, y = happyScore), color = "red",
              method = "lm", formula = y ~ x, se = TRUE)
```

## 4. Construct a response-prediction plot.

```{r}
plot(happyscore_income$happyScore ~ fitted(model1), xlab = "Prediction", ylab = "Response")
abline(0, 1)
```

## 5. Construct a response-residual plot.

```{r}
plot(resid(model1) ~ happyscore_income$happyScore, xlab = "Response", ylab = "Residuals")
abline(h=0)
```

## 6. Construct a residual plot by the number of observation.

```{r}
plot(c(1:length(happyscore_income$happyScore)), resid(model1), xlab = "Number of observation", ylab = "Residuals")
abline(h = 0)
```

## 7. Construct a Q-Q plot for the residuals.

```{r}
qqPlot(resid(model1))
```










